Over-relaxed Sinkhorn's Algorithm for Regularized Optimal Transport

### 2017-10-13 paper.tex
Algo

\end{remark}
{\color{blue} As the inequality is strict in U, $\gamma^*\notin U$.}

@@

In practice, we observed that the algorithm introduced in Theorem \ref{thm:algo} can be simplified and it is sufficient to check $F(P^\omega_{\Ccal_2}(P^\omega{\Ccal_1}(\gamma^l)))-F(\gamma^l)>0$ for realizing the over-relaxed iterations with parameter $\omega$.
The cost of this test is linear with respect to the data dimension (i.e. $o(n_1+n_2)$).

\renewcommand{\algorithmiccomment}[1]{(#1)}
\begin{algorithm}
\caption{Over-relaxed Sinkhorn algorithm}
\label{SOR}
\begin{algorithmic}
\REQUIRE $\mu^1\in \IR^{n_1}$, $\mu^2\in \IR^{n_2}$, $c\in \IR^{n_1\times n_2}_+$
\STATE Set $a=\mathbf{1}_{n_1}$, $b=\mathbf{1}_{n_2}$, $\gamma^0=e^{-c/\epsilon}$, $\omega\in[1;2[$ and $\eta>0$
\WHILE {$||a\otimes \gamma^0b-  \mu_1||>\eta$}
\STATE $\tilde a=\mu_1\oslash (\gamma^0 b)$, 
\STATE $\bar a=a^{1-\omega}\otimes \tilde a^\omega$
\STATE $\tilde b=\mu_2\oslash (^t\gamma^0 \bar a)$
\IF{ $\langle \mu^1,\phi_\omega(a\oslash\tilde a) \rangle +\langle \mu^2,\phi_\omega(b\oslash\tilde b)\rangle>0$}
\STATE  $a=\bar a$ and $b=b^{1-\omega}\otimes \tilde b^\omega$
\COMMENT{Over-relaxed Sinkhorn iteration}
\ELSE
\STATE $a=\mu_1\oslash (\gamma^0 b)$ and $b=\mu_2\oslash (^t\gamma^0 a)$  
\COMMENT{Sinkhorn iteration}
\ENDIF
\ENDWHILE
 \RETURN $\gamma=\diag(a)\gamma^0\diag(b)$
\end{algorithmic}
\end{algorithm}

>>>>

\end{remark}
{\color{blue} Comment: As the inequality is strict in U, $\gamma^*\notin U$.}

@@

In practice, we observed that the algorithm introduced in Theorem \ref{thm:algo} can be simplified and it is sufficient to check $F(P^\omega_{\Ccal_2}(P^\omega_{\Ccal_1}(\gamma^l)))-F(\gamma^l)>0$ for realizing the over-relaxed iterations with parameter $\omega$.
The cost of this test is linear with respect to the data dimension (i.e. $o(n_1+n_2)$).

\renewcommand{\algorithmiccomment}[1]{\hfill\bgroup(#1)\egroup}
\begin{algorithm}
\caption{Over-relaxed Sinkhorn algorithm}
\label{SOR}
\begin{algorithmic}
\REQUIRE $\mu^1\in \IR^{n_1}$, $\mu^2\in \IR^{n_2}$, $c\in \IR^{n_1\times n_2}_+$
\STATE Set $a=\mathbf{1}_{n_1}$, $b=\mathbf{1}_{n_2}$, $\gamma^0=e^{-c/\epsilon}$, $\omega\in[1;2[$ and $\eta>0$
\WHILE {$||a\otimes \gamma^0b-  \mu_1||>\eta$}
\STATE $\tilde a=\mu_1\oslash (\gamma^0 b)$,  $a_\omega=a^{1-\omega}\otimes \tilde a^\omega$
\STATE $\tilde b=\mu_2\oslash (^t\gamma^0  a_\omega)$
\IF{ $\langle \mu^1,\varphi_\omega(a\oslash\tilde a) \rangle +\langle \mu^2,\varphi_\omega(b\oslash\tilde b)\rangle>0$}
\STATE  $a=a_\omega$, $b=b^{1-\omega}\otimes \tilde b^\omega$\COMMENT{Over-relaxed Sinkhorn iteration}
\ELSE
\STATE $a=\tilde a$, $b=\mu_2\oslash (^t\gamma^0 a)$  \COMMENT{Sinkhorn iteration}
\ENDIF
\ENDWHILE
 \RETURN $\gamma=\diag(a)\gamma^0\diag(b)$
\end{algorithmic}
\end{algorithm}
